Rotating Stars from \Kepler Observed with Gaia DR2

### 2018-05-05 paper/ms.tex
update plots

In this paper

@@

\begin{figure*}[]
\centering
\includegraphics[width=6in]{../figures/cmd}
\caption{
color--magnitude diagram for 30,928 \Kepler stars included in Gaia DR2, colored by the rotation period measured from \citet{mcquillan2014}.}
\label{fig:cmd}
\end{figure*}

@@

\begin{figure*}[]
\centering
\includegraphics[width=3.5in]{../figures/rot_dist_0}
\includegraphics[width=3.5in]{../figures/rot_dist_350}
\includegraphics[width=3.5in]{../figures/rot_dist_525}
\includegraphics[width=3.5in]{../figures/rot_dist_600}
\includegraphics[width=3.5in]{../figures/rot_dist_900}
\caption{
}
%\label{fig:cmd}
\end{figure*}

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/B_V_rot}
\caption{
}
%\label{fig:cmd}
\end{figure}

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/delta_per}
\caption{
}
%\label{fig:cmd}
\end{figure}

\begin{figure*}[]
\centering
\includegraphics[width=6.5in]{../figures/cmd_zoom}
\caption{
}
%\label{fig:cmd}
\end{figure*}

>>>>

In this letter

@@

\begin{figure*}[]
\centering
\includegraphics[width=6in]{../figures/cmd}
\caption{
Color--magnitude diagram for 30,305 \Kepler stars from the \citet{mcquillan2014} sample that are included in Gaia DR2, colored by their measured rotation period. For reference we show a $10^9$ year MIST isochrone (black line) used to select likely main sequence, single stars (black line). A track of binary  stars is apparent $\sim$0.7 mag above the main sequence. As in \citet{davenport2017}, we find significant contamination of the rotation period sample for bluer stars by sub-giants.}
\label{fig:cmd}
\end{figure*}

@@

\begin{figure*}[]
\centering
\includegraphics[width=3.5in]{../figures/rot_dist_0}
\includegraphics[width=3.5in]{../figures/rot_dist_350}
\includegraphics[width=3.5in]{../figures/rot_dist_525}
\includegraphics[width=3.5in]{../figures/rot_dist_600}
\includegraphics[width=3.5in]{../figures/rot_dist_900}
\caption{Color--period diagrams for our sample of likely main sequence stars, divided into bins of distance. Our nearest bin (within 350pc) is effectively the distance analyzed in \citet{davenport2017} using Gaia DR1, and clearly shows the rotation period bimodality for the entire sample. The brighter magnitude limit of the \Kepler sample results in redder (fainter) stars missing in our further distance bins. The rotation period bimodality can be seen in the 350-525 pc bin, but is not found in the bluer stars at further distances.
}
\label{fig:color_period}
\end{figure*}

%\begin{figure}[]
%\centering
%\includegraphics[width=3.5in]{../figures/B_V_rot}
%\caption{converted to B-V using Padova isochrone colors. 3 gyrochrones from \citet{meibom2009} with ages 300 Myr (dark red), 600 Myr (bright red), and 1.2 Gyr (blue) are shown.
%}
%%\label{fig:cmd}
%\end{figure}
%

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/delta_per}
\caption{Histograms of the log rotation periods after a 600 Myr gyrochrone was subtracted for stars in the same five distance bins shown in Figure \ref{fig:color_period}.
}
\label{fig:per_hist}
\end{figure}

\begin{figure*}[]
\centering
\includegraphics[width=6.5in]{../figures/cmd_zoom}
\caption{
}
\label{fig:cmd_zoom}
\end{figure*}
